SPARQL on the Open, Decentralised Web

### 2016-06-24 dissertation/related.tex
Capitilize all see in footnotes
HTTP details

Under the auspices of the  World Wide Web Consortium a standard for
read-write applications using RDF has been developed: The Linked Data
Platform \cite{ldp1}. The abstract in the specification describes it
as:
\begin{quote}
Linked Data Platform (LDP) defines a set of rules for HTTP operations
on web resources, some based on RDF, to provide an architecture for
read-write Linked Data on the web.
\end{quote}
While developers who are familiar with HTTP-based applications and
Linked Data may feel familiar with the platform, it still requires
that they read and understand the specification to be able to use it,
and therefore, it is not hypermedia, and I think it misses out on many
of the benefits of hypermedia. A discussion at the Developers Workshop
at the Extended Semantic Web Conference 2015\footnote{see
  \url{https://www.youtube.com/watch?v=F4WN4XEpViA} for a recording of
  the discussion session.} found rough consensus around a comment
formulated by me:
\begin{quote}
LDP has to be superseded by hypermedia in some way.
\end{quote}

@@

The canonical labelling algorithm presented in this paper provides an
opportunity for further work, when considered in an HTTP context: The
\httph{ETag} header, defined in RFC7232 \cite{rfc7232}, can optionally
contain an opaque identifier for a specific version of a resource
representation, e.g. a SPARQL result. Such a canonical label could be
used in conjunction with an algorithm that tracks changes to the RDF
graph to produce an \httph{ETag}. For slow-changing Linked Data, which
is a common case, it is a possibility that a canonical label in
combination with a time-stamp of the entire RDF Graph could yield
considerable benefits. However, the presented algorithm does not cover
SPARQL in its entirety, for example, it does not handle named graphs,
solution modifiers and filters, nor is it clear how it handles
property paths (which in many cases should be trivial, since a
property path often has an equivalent Basic Graph Pattern). Union
queries or negation is also not mentioned, so more work is needed for
this method to have general applicability. Nevertheless, if the entire
Group Graph Pattern of a certain query is supported, and the query
projects all variables, e.g. it wraps the pattern with \sparql{SELECT
  *} or \sparql{CONSTRUCT}, the \httph{ETag} would be trivial to
construct using the presented algorithm in a non-trivial number of
beneficial cases. With this, cached result verification could be done
by a mediator using HTTP requests with the \httph{If-None-Match}
header and so make it possible to use parts of the engine of this
paper usable in the Internet infrastructure.

>>>>

Under the auspices of the  World Wide Web Consortium a standard for
read-write applications using RDF has been developed: The Linked Data
Platform \cite{ldp1}. The abstract in the specification describes it
as:
\begin{quote}
Linked Data Platform (LDP) defines a set of rules for HTTP operations
on web resources, some based on RDF, to provide an architecture for
read-write Linked Data on the web.
\end{quote}
While developers who are familiar with HTTP-based applications and
Linked Data may feel familiar with the platform, it still requires
that they read and understand the specification to be able to use it,
and therefore, it is not hypermedia, and I think it misses out on many
of the benefits of hypermedia. A discussion at the Developers Workshop
at the Extended Semantic Web Conference 2015\footnote{See
  \url{https://www.youtube.com/watch?v=F4WN4XEpViA} for a recording of
  the discussion session.} found rough consensus around a comment
formulated by me:
\begin{quote}
LDP has to be superseded by hypermedia in some way.
\end{quote}

@@

The canonical labelling algorithm presented in this paper provides an
opportunity for further work, when considered in an HTTP context: The
\httph{ETag} header, discussed in Section~\ref{sec:httpcache}, can be
used for a SPARQL result. Such a canonical label could be
used in conjunction with an algorithm that tracks changes to the RDF
graph to produce an \httph{ETag}. For slow-changing Linked Data, which
is a common case, it is a possibility that a canonical label in
combination with a time-stamp of the entire RDF Graph could yield
considerable benefits. However, the presented algorithm does not cover
SPARQL in its entirety, for example, it does not handle named graphs,
solution modifiers and filters, nor is it clear how it handles
property paths (which in many cases should be trivial, since a
property path often has an equivalent Basic Graph Pattern). Union
queries or negation is also not mentioned, so more work is needed for
this method to have general applicability. Nevertheless, if the entire
Group Graph Pattern of a certain query is supported, and the query
projects all variables, e.g. it wraps the pattern with \sparql{SELECT
  *} or \sparql{CONSTRUCT}, the \httph{ETag} would be trivial to
construct using the presented algorithm in a non-trivial number of
beneficial cases. With this, cached result verification could be done
by a mediator using HTTP requests with the \httph{If-None-Match}
header and so make it possible to use parts of the engine of this
paper usable in the Internet infrastructure.
